\cvsection{Projects}

% 552: blockchain application, 573: 4 , 587: c++ java.  572: AI, Monte Carlo 535, page ranking, java. 577: 559: 661: word2vec

% data visulization, ali tianchi

% contest, robot, c: file compression.


\begin{cventries}
  \cventry
    {ISU Term Project} % Empty position
    {Crop Insurance Dapp: Design and Implementation} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {A decentralized application (Dapp) based on \textbf{BlockChain} to solve inefficiency, fraud, human error and cyberattacks in crop insurance. }
        \item {Provide web interface to farmers, insurance agents and third party participants like weathers, markets, governments, etc. (\textbf{Web3, HTML/CSS, JS}). }
        \item {Setup and maintain a blockchain with \textbf{Ganache} to store participants' information and transaction records. }
        \item {Design and deploy smart contract for every participant in \textbf{Solidity}. }
      \end{cvitems}
    }

  \cventry
    {ISU Term Project} % Empty position
    {Deep Learning-based Self-learning Checkers Game Agent} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Design and implement a \textit{checkers} game agent. The agent is expected to learn by playing a large number of iterations of the game against designed opponents and itself. The MOVE is decided an evaluator which is a three layer neural network. (\textbf{Python})}
        \item {Design and implement the opponent agent with Monte Carlo Search Tree. (\textbf{Python})}
        \item {Design and implement a graphic user interface so that the designed agent could play and learn from real people. (\textbf{wxPython})}
      \end{cvitems}
    }

  \cventry
    {Chinese Academy of Science Term Project} % Empty position
    {Public opinion analysis and visualization} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {This project analysis millions of posts and comments downloaded from \textit{weibo} (Chinese) in certain period of time, say ten minutes, and visualize the trend of public opinion. }
        \item {Develop a web service with \textbf{Flask}. It process posts and comments at backend and reply to frontend with processed data. (\textbf{Flask, Python})}
        \item {Visualize public opinion with d3 library and add user interaction to provide more flexible and necessary data to users. (\textbf{d3, HTML/JS})}
      \end{cvitems}
    }
\end{cventries}
