\cvsection{Research Experience}

% nlp : mpu , reinforcement learning , entity recognition,

% image processing: hdr and tone mapping, c++ implimentation

% voice location. mips cpu.

\begin{cventries}
  \cventry
    {Research Assistant}
    {Multi-class Positive \& Unlabeled (MPU) Learning for Named Entity Recognition}
    {Ames, IA, US}
    {May, 2019 -- January, 2020}
    {
      % \begin{cvparagraph}
      %   This work provide a method to train one model from positive and unlabeled dataset which could tackle multi-class classification problem. The applicaion is build for named entity recognition, which is a common task in NLP.
      % \end{cvparagraph}
      % \vspace{1.5mm}
      \begin{cvitems}
        \item {Derived the risk function for MPU and found suitable loss function that level up the performance of the trained model. }
        \item {Rewrite the code in \textbf{OOP} style which upgrade the code scalability to new datasets and models. (\textbf{Python})}
        \item {Deployed and run the program on pronto server (\textbf{slurm} job scheduler installed) to train a high performance model. }
      \end{cvitems}
    }
  \cventry
    {Research Assistant}
    {High Dynamic Range (HDR) Image Processing}
    {Beijing, China}
    {July, 2014 -- July, 2017}
    {
      \begin{cvitems}
        \item {Designed and implemented camera array and corresponding HDR algorithm to capture and show HDR images on Sandroid Cubesat (a 2U Cubesat with smart phones as computing core).}
        \item {Simulated the algorithm in \textbf{MatLab} and proved the feasibility of our design.}
        \item {Implemented the algorithm in \textbf{C/C++} and build a dynamic linking library for further usage. }
      \end{cvitems}
    }
    
  \cventry
    {Student Researcher}
    {The source localization of human voice via non-directional microphone array.}
    {Hefei, Anhui, China}
    {July, 2011 -- December, 2011}
    {
      \begin{cvitems}
        \item {Designed and implemented the phone array, embedded system (Stm32 with ARM architecture) and corresponding algorithm to localize human voice}
        \item {Simulated the algorithm in \textbf{MatLab} and proved the feasibility of our design.}
        \item {Implemented the algorithm in \textbf{embedded C/C++} and build a dynamic linking library for further usage. }
      \end{cvitems}
    }
  % \cventry
  %   {Recommendation System, Imaging processing, Data Science} % Degree
  %   {Research experience} % Institution
  %   {} % Location
  %   {} % Date(s)
  %   {}
  %
  % \cventry
  %   {Big Data, Machine Learning, NLP} % Degree
  %   {Now interested} % Institution
  %   {} % Location
  %   {} % Date(s)
  %   {}
  % \textbf{Experience} : Recommendation System, Imaging processing, Data Science
  %
  % \textbf{interest} : Big Data, Machine Learning, NLP

\end{cventries}
